Building a Large-Scale Cross-Lingual Knowledge Base from Heterogeneous Online Wikis

### 2015-06-07 nlpcc/paper.tex
提交版本

\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
\usepackage{CJK}
\usepackage{url}
\usepackage[ruled]{algorithm2e}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{multirow}

\usepackage{xeCJK}
%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
\setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
\setCJKsansfont[BoldFont=STHeiti]
\setCJKmonofont{STFangsong}
%\usepackage{CJKutf8}

@@

\title{Building Large-Scale Cross-Lingual Knowledge Base from Heterogeneous Online Wikis}
%\titlerunning{Bilingual Knowledge Base}
%\author{Mingyang Li$^\dag$ \and Yao Shi$^\dag$ \and Zhigang Wang$^\dag$}
%\authorrunning{Mingyang Li et.al}

@@

\begin{abstract}
Cross-lingual Knowledge Bases are important for global knowledge sharing. However, there are few Chinese-English knowledge bases due to the following reasons: 1) the scarcity of Chinese knowledge; 2) the number of current cross-lingual language links is limited; 3) the incorrect relation in semantic taxonomy. In this paper, a large-scale cross-lingual knowledge base(CLKB) is build to solve the above problems. The CLKB is based on English and Chinese Wikipedia as well as Baidu Baike and Hudong Baike. An extension method is used to increase language links while a pruning approach is used to refine taxonomy. Totally, there are 663,740 classes, 11,721,238 instances, 56,449 properties referred in the CLKB. Among of them, 507,042 items are cross-lingual linked. To the best of our knowledge, it's the first large-scale Chinese-English knowledge base with balanced knowledge quantity. Moreover, the paper provides visualization of knowledge and a SPARQL endpoint accessing to the established CLKB.

\keywords{Knowledge Base, Semantic Web, Taxonomy, Cross-lingual}
\end{abstract}

\section{Introduction}
As the Web is evolving to a highly globalized information space, sharing knowledge across different languages is attracting increasing attentions. Multilingual knowledge bases have significant applications such as multi-lingual information retrieval, machine translation and deep question answering. DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}}, is a multi-lingual multi-domain knowledge base and becomes the nucleus of LOD\footnote{{\tt http://linkeddata.org/}}. Obtained from the automatic integration of WordNet\footnote{{\tt http://wordnet.princeton.edu/}} and Wikipedia, YAGO, MENTA and BabelNet are other famous large multi-lingual knowledge bases.

However, most non-English knowledge in those knowledge bases is pretty scarce. Figure \ref{fig_stat} shows a simplified long tail distribution of the number of articles on six major Wikipedia language versions. Due to the imbalance of different Wikipedia language versions, the knowledge distribution across different languages is highly unbalanced in those knowledge bases which are generated from Wikipedia. For instance, DBpedia contains 4.58 million English instances but even no Chinese dataset published. On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 6 million articles, are even larger than the English Wikipedia. If a knowledge base could be established between English Wikipedia and Chinese Hudong Baike, an Chinese-English knowledge base with much higher coverage in Chinese can be constructed.

@@

To enrich the Chinese knowledge, we try to build a large-scale Chinese-English knowledge base by semantifying four heterogeneous online wikis, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike. In this paper, we propose a unified framework to build such a knowledge base. The framework contains three steps: extracting dataset from online wikis, extending an initial language link set, and pruning taxonomy for more precise semantic relation. The generated knowledge base contains 663,740 classes, 11,721,238 instances and 56,449 properties. An online system supporting keyword search and SPARQL endpoint is also developed.

This non-trivial task poses the challenges as follows:
\begin{enumerate}
  \item The cross-lingual links are highly limited inside Wikipedia. For instance, there are only 9\% Chinese-English matched articles in Wikipedia in all articles. How could we find enough Chinese-English \verb"owl:sameAs" relations?
  \item The subsumption relations of the online wikis' category systems contain lots of noise. For example, in English Wikipedia "Wikipedia-books-on-people", which is actually \verb"subClassOf" "Books", is taken as the sub-category of "People" mistakenly. How could we detect those incorrect semantic relations?
\end{enumerate}

Driven by these challenges, we propose a unified framework to build a Chinese-English knowledge base from four heterogeneous online wikis. Specifically, our work makes the following contributions.
\begin{enumerate}
  \item We achieve refined datasets from multiple heterogeneous online wikis through unified extracting process.
  \item We extend cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
  \item We prune the original taxonomy, which is extracted from wiki category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations.
  \item Both online-system and SPARQL endpoint are provided for public query operations over our knowledge base.
\end{enumerate}

The rest of the paper is organized as follows. Section \ref{sec:pd} presents some basic concepts and the problem formulation. In Section \ref{sec:sde} we present detailed approaches. Section \ref{sec:cli} describes cross-lingual integration. The experimental results are reported in Section \ref{sec:result}. Some related work are given in Section \ref{sec:work}. Finally we conclude our work in Section \ref{sec:con}.

\section{Preliminaries}
\label{sec:pd}
In this section, we give definitions about our knowledge base and describe the task in this work.

\subsection{Basic Concepts}
\para{Online Wikis.} Nowadays, Wikipedia is the largest data store of human knowledge. It was launched in 2001 and has hold over 35 million articles in 288 languages by 2015. Out of these, English articles contribute most. The imbalance of different language articles makes ontologies based on Wikipedia-only behave badly in cross-lingual. Thus, more Chinese sources are necessary to enrich Chinese source.

Among the large-scale monolingual Chinese wikis currently, Baidu Baike and Hudong Baike are the most content-rich. Hudong Baike was founded in 2005 and contains more than 12 million articles with about 9 million experts' contribution until 2015. Meanwhile, Baidu Baike maintains more than 11 million articles.

Here, we consider an encyclopedia wiki as a collection of articles, category system, which can be defined as: $W = <A,C>$, where A denotes articles, C denotes categories in W.

\para{Wiki Pages.} Articles from the wiki sources are similar in structure. Usually they provide two important elements with potential semantic information, category system and articles. A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}. An article describes an entity with rich information. Each article is linked to one or more categories by \textit{articleOf} relation. In general, six elements can be exploited in each article page:
%\begin{figure}
%    \centering
%    \begin{minipage}[t]{0.8\textwidth}
%        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
%        \caption{Taxonomy in Hudong}
%        \label{fig:hudong-taxonomy}
%    \end{minipage}%
%\end{figure}
\begin{itemize}
  \item Title: A Title is the label of an entity, whose uniqueness can be used to distinguish entities.
  \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article.
  \item Infobox: Most of articles contain infobox. An infobox maintains structured data in subject-attribute-value format.
  \item Link: Links are entries to other articles within the wiki. They represent the relations between the current article and others.
  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
  \item URL: Each article has an HTTP url to identify itself on web.
\end{itemize}

%Fig. \ref{fig:interstellar} shows a snap of an article in Chinese Wikipedia.
%\begin{figure}[ht]
%    \centerline{\includegraphics[width=1\columnwidth]{fig/interstellar}}
%    \caption{A snap of Interstellar(Film) article in Chinese Wikipedia}
%    \label{fig:interstellar}
%\end{figure}%
%
An article $a$ can be defined as follow:
\begin{equation}
    a = <Ti(a),Ab(a),Li(a),In(a),C(a),U(a)>
\end{equation}
where $Ti(a),Ab(a),Li(a),In(a),C(a),U(a)$ denotes title, abstract, links, infobox, category tags, url of article $a$.

Notably, articles in Wikipedia follow templates specified by Wikipedia when being edited. A template defines items that a group of article should fill. Besides, infoboxes are also generated based on certain templates recommended by Wikipedia. For example, The infobox in film 冰雪奇缘(Frozen) is edited according to the Template \emph{Infobox film}, which maintains a property set of films. An infobox $In(a)$ contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}. We denote infobox template used in article $a$ as $T(a)$. Templates specify certain attributes, which are usually different from those displayed on the webpage. Thus, we define an attribute-value pair as a triple $p=<tl,dl,v>$, where $tl$ is attribute label in template, $dl$ is displayed label in web page and $v$ is the corresponding value. The value maybe a text or a reference to another entity.

Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version articles. %Fig. \ref{fig:interstellar} shows language links of \emph{Interstellar} on the left column of the Wikipedia page.
As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denote the article's language links in English and Chinese. To a $cl \in CL$, $cl(a) = <L_{z}(a), L_{e}(a)>$.

\para{Knowledge Base} A knowledge base is a formal specification of a group of entities. Our knowledge base is described as a 4-tuple:
\begin{equation}
    KB = <C,I,P,H^C>
\end{equation}
where $C$, $I$, $P$ are the sets of classes, instances, and properties, respectively. $H^C$ represents the hierarchical relationships of classes. The taxonomy of our knowledge base includes four types of relationships, which are \textit{subClassOf} of class-class, \textit{instanceOf} of class-instance, \textit{relatedClassOf} of instance and related class, \textit{relatedTopicOf} of class and related topic.

A Cross-lingual Knowledge Base(CLKB) is a database conform to a cross-lingual ontology. Taking advantage of language links in $CL$, several monolingual knowledge bases generated from various sources can be merge into one.  Thus our Chinese-English knowledge base can be defined as:
\begin{equation}
    CLKB = <KB_{z}, KB_{e}>
\end{equation}
where $KB_{z}$ and $KB_{e}$ denote the monolingual knowledge base in Chinese and English. CLKB combines the two according to $CL$.

\para{Cross-lingual Knowledge Base Building} In this paper, our task is to build a CLKB assembling knowledge from several English or Chinese wiki sources. Given an online-wiki $W_{i}$, we get dataset including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each $W_{i}$ by extraction. We then enrich the extracted cross-lingual link set $CL$ using an link-discovery extension method. We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship. Our final output is an Chinese-English CLKB though process of combining $KB_{z}$ and $KB_{e}$ by utilizing language links in $CL$.

The whole building procedure is shown in Fig. \ref{fig:procedure}. We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia. Because of heterogeneity, various extractors should be employed. After data parsing, we delete incorrect semantic relations by going through taxonomy pruning. At last, using the extended cross-lingual links, we combine the four dataset into our CLKB.

\vspace{-0.5cm}
\begin{figure}[ht]
    \centerline{\includegraphics[width=1\columnwidth]{fig/procedure2}}
    \caption{Procedure of Building Our Cross-lingual Knowledge Base}
    \label{fig:procedure}
\end{figure}
\vspace{-0.5cm}

@@

However, the whole taxonomy can not directly transform from category system due to the following problems:
\begin{itemize}
    \item There are auxiliary categories in Wikipedia, which help arrange specific articles or category pages. For example, \emph{Lists of artists} or \emph{Food templates}.
    %s\item Some sub-category links in the category system maybe inconsistent. Some categories may contain itself as sub-category, or contain sub-category that also be the super-category of it. As Fig. \ref{fig:category-mistakes} shows: In Hudong, the sub-category of 国家元首(Head of State) contains itself as a child, which causes a circle in taxonomy tree. Meanwhile, in Wikipedia, \textcolor{red}{例子}
    \item Some categories relate to only one article. According to the definition of class, such categories are less representative to a group of instances, therefore it's unwise to retain them as classes.
\end{itemize}

@@

\subsection{Property Extraction}
\label{sec:pe}
A property is defined as an attribute of an entity. It represents the relation between an instance and its value. We divided properties into two types: object property, whose value is an individual, such as 导演(directed by); datatype property, whose value is a literal text, such as 生日(birth date). Considering both content and infobox of an article, we extract two kinds of properties, General-properties and Infobox-properties.

@@

\para{Infobox-properties.} Attributes acquired from infobox are considered as infobox properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox. The type of a property, datatype or object, depends on the type of the value. Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as object. For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string. Meanwhile, 导演(directed by) is an object property because its value points to a person who directed the movie.

We are challenged when extracting properties from infoboxes:
\begin{itemize}
    \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with it in the published dump file. Fig.\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Frozen's} infobox. The left is infobox, the middle is a glance from dump file in Wikipedia. We explore the display labels as property labels in Wikipedia rather than dump labels extracted from raw data.
    \begin{figure}[ht]
        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
        \label{fig:infobox-template}
    \end{figure}%
\item There are special characters in labels. Wikipedia usually uses hyphen "-" or dot "•" to mark sublabels. For example, attribute \emph{population} property has sub-properties "-Density" and "-Urban". In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
\end{itemize}

To solve the problems above, we take advantage of template information. Specifically, Wikipedia institutes rules of rendering label in templates. Right of Fig.\ref{fig:infobox-template} shows an example of \emph{Template:Infobox film}, where corresponding relations of display labels and dump labels come from. When a dump label occurs in dump file, we replace it by its mapping display label.

\subsection{Instance Extraction}
\label{sec:ie}
An article describes unique entity in the world. Therefore we can extract an article as an instance. During the extraction, illustrative or structure-related articles in Wikipedia are deleted, including category list pages and template documentations.

We harvest four types of information during this stage. (1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value; (2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page. For example, 美国电影作品(American films) is a category of 冰雪奇缘(Frozen); (4) Reference relation with other instances according to links in the content, such as 冰雪女王(The Snow Queen).

@@

To construct a CLKB with existing structured data, firstly we increase cross-lingual links, which can help match the same entity in two languages. Secondly, we integrate this four wikis, that is, respectively merging classes, instances and properties from the four sources if they represent the same thing. Thirdly, we prune the taxonomy generated from class relationships to make it more accurate.

\subsection{Cross-lingual Linking}
There are 227 thousand cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances. Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set. With the linkage factor graph model, we harvest a cross-lingual links extension as many as 215 thousand with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.

However, due to using templates, Infobox-properties have no obvious cross-lingual links. Thus, we take the following steps to acquire property links:
\begin{enumerate}
    \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label. That is to say, to $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
    \item Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$ direct to the same entity, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label;
    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; for object properties, check whether the value refer to the same entity.
\end{enumerate}

In order to make all wikis link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers. For instance, we merge instances by the following steps: (1) Merge all instances extracted from Chinese wikis by instance title. (2) To a $L_{z}$, find whether there is an English cross-lingual link $L_{e}$ in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID, else number it with a new ID.

@@

As a result of combining multi-source information without verifying, there is noise in taxonomy. %For example:
Therefore, we introduce the method from \cite{wang2014cross} to detect the correct \textit{subClassOf} and \textit{instanceOf} relations from \textit{subCategoryOf} and \textit{articleOf}. %Table. \ref{tab:} shows some examples of correct relations.
In particular, some language-dependent literal and language-independent structural features are defined to vectorize each class or instance. Employing these features, a Yes-or-No binary-classification model is trained based on Logistic Regression. The whole process is iterative by retraining model with assured result to get higher precision. The prediction results are validated by cross-lingual information.

@@

To retain integrity of semantic relation, we define two types of new relations: \textit{relatedClassOf} for cut class-instance relations and \textit{relatedTopicOf} for cut class-class relations.

\section{Result}
\label{sec:result}

>>>>

\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
\usepackage{url}
\usepackage[ruled]{algorithm2e}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{multirow}

%\usepackage{CJK}

\usepackage{xeCJK}
%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
\setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
%\setCJKmonofont{STFangsong}
%\usepackage{CJKutf8}

@@

\title{Building a Large-Scale Cross-Lingual Knowledge Base from Heterogeneous Online Wikis}
%\titlerunning{Bilingual Knowledge Base}
%\author{Mingyang Li$^\dag$ \and Yao Shi$^\dag$ \and Zhigang Wang$^\dag$}
%\authorrunning{Mingyang Li et.al}

@@

\begin{abstract}
Cross-lingual Knowledge Bases are important for global knowledge sharing. However, there are few Chinese-English knowledge bases due to the following reasons: 1) the scarcity of Chinese knowledge; 2) the limited number of current cross-lingual language links; 3) the incorrect relation in semantic taxonomy. In this paper, a large-scale cross-lingual knowledge base(CLKB) is built to solve the above problems. Particularly, the CLKB integrates four online wikis including English Wikipedia, Chinese Wikipedia, Baidu Baike and Hudong Baike to balance the knowledge volume in different languages, employs a link-discovery method to augment the language links, and introduce a pruning approach to refine taxonomy. Totally, CLKB harvests 663,740 classes, 56,449 properties, 10,856,042 instances, among of which, 507,042 entities are cross-lingually linked. To the best of our knowledge, it's the first large-scale Chinese-English knowledge base with balanced knowledge quantity. At last, we provide a knowledge-display system supporting two ways to access the established CLKB, namely a keyword search box and a SPARQL endpoint.

\keywords{Knowledge Base, Cross-lingual Linking, Taxonomy Pruning}
\end{abstract}

\section{Introduction}
As the Web is evolving to a highly globalized information space, sharing knowledge across different languages is attracting increasing attentions. Multi-lingual knowledge bases have significant applications such as multi-lingual information retrieval, machine translation and deep question answering. DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}}, is a multi-lingual multi-domain knowledge base and becomes the nucleus of Linked Open Data\footnote{{\tt http://linkeddata.org/}}. Obtained from the automatic integration of WordNet\footnote{{\tt http://wordnet.princeton.edu/}} and Wikipedia, YAGO, MENTA and BabelNet are other famous large multi-lingual knowledge bases.

However, most non-English knowledge in those knowledge bases is pretty scarce. Fig. \ref{fig_stat} shows a simplified long tail distribution of the number of articles on six major Wikipedia language versions. Due to the imbalance of different Wikipedia language versions, the knowledge distribution across different languages is highly unbalanced in those knowledge bases which are generated from Wikipedia. For instance, DBpedia contains 4.58 million English instances but even no Chinese dataset published. On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 11 million articles, are even larger than the English Wikipedia. If a knowledge base could be established between English Wikipedia and Chinese Hudong Baike, an Chinese-English knowledge base with much higher coverage in Chinese can be constructed.

@@

To enrich the Chinese knowledge, we try to build a large-scale Chinese-English knowledge base by semantifying four heterogeneous online wikis, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike. This non-trivial task poses the challenges as follows:
\begin{enumerate}
  \item The cross-lingual links are highly limited inside Wikipedia. For instance, there are only 9\% Chinese-English matched articles in Wikipedia in all articles. How could we find enough Chinese-English \verb"owl:sameAs" relations?
  \item The subsumption relations of the online wikis' category systems contain lots of noise. For example, in English Wikipedia ``Wikipedia-books-on-people", which is actually \verb"subClassOf" ``Books", is taken as the sub-category of ``People" mistakenly. How could we detect those incorrect semantic relations?
\end{enumerate}

Driven by these challenges, we propose a unified framework to build a Chinese-English knowledge base from four heterogeneous online wikis. The framework contains three steps: extracting dataset from online wikis, extending an initial language link set, and pruning taxonomy for more precise semantic relations. The generated knowledge base contains 663,740 classes, 56,449 properties and 10,856,042 instances. Specifically, we make the following contributions:
\begin{enumerate}
  \item We extend cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and by analyzing templates in Wikipedia for property.
  \item We prune the original taxonomy, which is extracted from wiki category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations.
  \item An online-system supporting keyword search and SPARQL endpoint is provided for public query operations over our knowledge base.
\end{enumerate}

The rest of the paper is organized as follows. Section \ref{sec:pd} presents some basic concepts and the problem formulation. In Section \ref{sec:sde} we introduce detailed extraction approaches. Section \ref{sec:cli} describes cross-lingual integration. The experimental results are reported in Section \ref{sec:result}. Some related work are given in Section \ref{sec:work}. Finally we conclude our work in Section \ref{sec:con}.

\section{Preliminaries}
\label{sec:pd}
In this section, we give definitions about our knowledge base and describe our task.

%\subsection{Basic Concepts}
\para{Online Wikis.} Nowadays, Wikipedia is the largest data store of human knowledge. It was launched in 2001 and has hold over 35 million articles in 288 languages by 2015. Out of these, English articles contribute most.

Baidu Baike and Hudong Baike are the most content-rich among the large-scale monolingual Chinese wikis currently. Hudong Baike was founded in 2005 and contains more than 12 million articles with about 9 million experts' contribution until 2015. Meanwhile, Baidu Baike maintains over 11 million articles.

\para{Wiki Pages.} Articles from the wiki sources are similar in structure. Usually they provide two important elements with potential semantic information, category system and articles. Here, we define an encyclopedia wiki as: $W = <C,A>$, where $C$ denotes categories, $A$ denotes articles in $W$. A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}. An article describes an entity with rich information. In general, six elements can be exploited in each article page:
%\begin{figure}
%    \centering
%    \begin{minipage}[t]{0.8\textwidth}
%        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
%        \caption{Taxonomy in Hudong}
%        \label{fig:hudong-taxonomy}
%    \end{minipage}%
%\end{figure}
\begin{itemize}
  \item Title: A Title is the label of an entity, whose uniqueness can be used to distinguish entities.
  \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article.
  \item Infobox: Most of articles contain infobox. An infobox maintains structured data in attribute-value format.
  \item Link: Links are entries to other articles within the wiki. They represent the relations between the current article and others.
  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
  \item URL: Each article has an HTTP url to identify itself on web.
\end{itemize}

%Fig. \ref{fig:interstellar} shows a snap of an article in Chinese Wikipedia.
%\begin{figure}[ht]
%    \centerline{\includegraphics[width=1\columnwidth]{fig/interstellar}}
%    \caption{A snap of Interstellar(Film) article in Chinese Wikipedia}
%    \label{fig:interstellar}
%\end{figure}%
%
An article $a$ can be defined as follow:
\begin{displaymath}
    a = <Ti(a),Ab(a),Li(a),In(a),C(a),U(a)>
\end{displaymath}
where $Ti(a),Ab(a),Li(a),In(a),C(a),U(a)$ denotes title, abstract, links, infobox, category tags, url of article $a$.

Notably, infoboxes in articles are generated based on certain templates recommended by Wikipedia. An infobox template collects attributes describing similar entities. For example, content in infobox of film 冰雪奇缘(Frozen) is normalized by \emph{Template:Infobox film}, which maintains a property set of films. We denote the infobox template used in article $a$ as $T(a)$. However, attribute labels in templates are usually different from those displayed on the webpage. Thus, we define an attribute as a triple $p=<tl,dl,v>$, where $tl$ is attribute label in template, $dl$ is display label in web page and $v$ is the corresponding value. The value maybe a text or a reference to another entity.

\para{Cross-lingual Links.} In Wikipedia, some article pages have language links which help readers switch to other language-version articles. %Fig. \ref{fig:interstellar} shows language links of \emph{Interstellar} on the left column of the Wikipedia page.
As for an entity containing both Chinese article $a_{z}$ and English article $a_{e}$ in Wikipedia, $L_{z}$ and $L_{e}$ denote the entity's language links in Chinese and English. For a $cl \in CL$, $cl(a) = <L_{z}(a_{z}), L_{e}(a_{e})>$.

\para{Knowledge Base.} A knowledge base is a formal specification of a group of entities. Our knowledge base is described as a 4-tuple:
\begin{displaymath}
    KB = <C,I,P,H^C>
\end{displaymath}
where $C$, $I$, $P$ are the sets of classes, instances, and properties, respectively. $H^C$ represents the hierarchical relationships of classes.

Our knowledge base includes four kinds of semantic relation, which are \textit{subClassOf} of class-class, \textit{instanceOf} of class-instance, \textit{relatedClassOf} of instance and related class, \textit{relatedTopicOf} of class and related topic.

A Cross-lingual Knowledge Base(CLKB) is a database conform to a cross-lingual ontology. Taking advantage of language links in $CL$, several monolingual knowledge bases generated from various sources can be merge into one.  Thus our Chinese-English knowledge base is defined as:
\begin{displaymath}
    CLKB = <KB_{z}, KB_{e}>
\end{displaymath}
where $KB_{z}$ and $KB_{e}$ denote the monolingual knowledge base in Chinese and English. CLKB combines the two according to $CL$.

\para{Cross-lingual Knowledge Base Building.} In this paper, our task is to build a CLKB assembling knowledge from several English or Chinese wiki sources. Given an online-wiki $W_{i}$, we get dataset including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, class hierarchical relationships $H^C_{i}$ of $W_{i}$ by extraction. We then enrich the existing cross-lingual link set $CL$ using a link-discovery method. We also refine taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship. Our final output is a Chinese-English CLKB through process of combining $KB_{z}$ and $KB_{e}$ by utilizing language links in $CL$. The whole procedure is shown in Fig. \ref{fig:procedure}. 
%We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia. Because of heterogeneity, various extractors should be employed. After data parsing, we delete incorrect semantic relations by going through taxonomy pruning. At last, using the extended cross-lingual links, we combine the four dataset into our CLKB.

\begin{figure}[ht]
    \centerline{\includegraphics[width=1\columnwidth]{fig/procedure2}}
    \caption{Procedure of Building Our Cross-lingual Knowledge Base}
    \label{fig:procedure}
\end{figure}

@@

However, the whole taxonomy can not directly transform from category system due to the following problems:
\begin{itemize}
    \item There are auxiliary categories in Wikipedia, which help arrange specific articles or category pages. For example, \emph{Lists of artists} or \emph{Food templates}.
    %s\item Some sub-category links in the category system maybe inconsistent. Some categories may contain itself as sub-category, or contain sub-category that also be the super-category of it. As Fig. \ref{fig:category-mistakes} shows: In Hudong, the sub-category of 国家元首(Head of State) contains itself as a child, which causes a circle in taxonomy tree. Meanwhile, in Wikipedia, \textcolor{red}{例子}
    \item Some categories relate to only one article. According to the definition of class, such categories are less representative types, therefore it's unwise to retain them as classes.
\end{itemize}

@@

\subsection{Property Extraction}
\label{sec:pe}
A property is defined as an attribute of an entity. It represents the relation between an entity and its value. We divide properties into two types: object property, whose value is an individual, such as 导演(directed by); datatype property, whose value is a literal text, such as 生日(birth date). Considering both content and infobox of an article, we extract two kinds of properties, General-properties and Infobox-properties.

@@

\para{Infobox-properties.} Attributes acquired from infobox are considered as infobox properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox. The type of a property, datatype or object, depends on the type of the value. Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as object. For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string. On the other hand, 导演(directed by) is an object property because its value points to a person who directed the movie.

We are challenged when extracting properties from infoboxes:
\begin{itemize}
    \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with that in the published dump file. Fig. \ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Frozen's} infobox. The left is infobox, the middle is a glance from dump file in Wikipedia. The attribute label 主演 displayed on webpage is different from label \emph{starring} extracted from dump data. However, we generally consider the display label rather than extracted label as a property label.
    \begin{figure}[ht]
        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
        \caption{Comparison of display label and dump label in \emph{Frozen} infobox}
        \label{fig:infobox-template}
    \end{figure}%
\item There are special characters in labels. Wikipedia usually uses hyphen ``-" or dot ``•" to mark sublabels. For example, attribute \emph{population} property has sub-properties ``-Density" and ``Urban". In addition, colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
\end{itemize}

To solve the problems above, we take advantage of template information. Specifically, Wikipedia institutes rules of rendering label in templates. Right of Fig. \ref{fig:infobox-template} shows an example of \emph{Template:Infobox film}, where relations of display labels and dump labels come from. When a dump label occurs in dump file, we replace it by its mapping display label.

\subsection{Instance Extraction}
\label{sec:ie}
An article describes a unique entity in the world. Therefore we can extract an article as an instance. During the extraction, illustrative or structure-related articles in Wikipedia are deleted, including category list pages and template documentations.

We harvest four types of information during this stage. (1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value; (2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page. For example, 冰雪奇缘(Frozen) is an article of category 美国电影作品(American films); (4) Reference relation with other instances according to links in the content, such as 冰雪女王(The Snow Queen).

@@

To construct a CLKB with obtained structured data, firstly we argument cross-lingual links, which can help match the same entity in two languages. Secondly, we integrate this four wikis, that is, respectively merging classes, instances and properties from the four sources if they represent the same thing. Thirdly, we prune the taxonomy generated from class relationships to make it more accurate.

\subsection{Cross-lingual Linking}
We follow two ways to get cross-lingual links for class, instance and property. One is extracting links according to Wikipedia language links for class and instance, the other is achieving links using infobox templates for property.

There are 227 thousand cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances. Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set. With the linkage factor graph model, we harvest a cross-lingual links extension as many as 215 thousand with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.

However, due to using templates, Infobox-properties have no obvious cross-lingual links. Thus, we take the following steps to acquire property links:
\begin{enumerate}
    \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same template label. That is, for $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
    \item Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label;
    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; for object properties, check whether the value refer to the same entity.
\end{enumerate}

In order to make all wikis link to each other, we unify the same class, instance and property from four sources, and give them unique identifiers. For instance, we merge instances by the following steps: (1) Merge all instances extracted from Chinese wikis by instance title. (2) To an $L_{z}$, find whether there is an English cross-lingual link $L_{e}$ in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID, otherwise number it with a new ID.

@@

%As a result of combining multi-source information without verifying, there is noise in taxonomy. %For example:
There is inevitably noise in the taxonomy since we combine multi-source information without verification. Therefore, we introduce the method from \cite{wang2014cross} to detect the correct \textit{subClassOf} and \textit{instanceOf} relations from \textit{subCategoryOf} and \textit{articleOf}. %Table. \ref{tab:} shows some examples of correct relations.
In particular, some language-dependent literal and language-independent structural features are defined to vectorize each class or instance. Employing these features, a binary-classification model is trained based on Logistic Regression. The whole process is iterative by retraining model with assured result to get higher precision. Moreover, the prediction results are validated by cross-lingual information.

@@

To retain integrity of semantic relation, we define two types of new relations: \textit{relatedClassOf} for cut class-instance relations and \textit{relatedTopicOf} for pruned class-class relations.

\section{Result}
\label{sec:result}
Here we show statistic results of our CLKB and introduce the system based on the knowledge base.
